\LARGE \bf Eye tracking with Educational Robots: A Cautionary Tale

### 2014-10-02 paper.tex
Reorganisation of the paper for HRI 'Enabling methods'

\section{Related Work: Gaze patterns and Expertise/Task based performance}

@@

\section{Experiment}

@@

\section{Results}

@@

\subsection{Average fixation duration on the robot during observation phase
vs.~condition}

@@

\subsection{First improvement vs.~condition}

@@

\subsection{Average fixation duration on the reference side during interaction
phase vs.~condition}

@@

\subsection{First improvement vs number of fixations on reference side}

>>>>

\section{State of Eye Tracking in Human-Robot Interaction}

\subsection{Eye Tracking as an Interaction Modality}

\subsection{Eye Tracking as a tool to Measure Joint Attention}

\section{Eye Tracking as a Tool for Assessing Social Interaction}

\subsection{Gaze patterns and Expertise/Task based performance}

@@

\section{Method Description}

\section{Field of Application and Deployment}

\section{Method Application}

@@

\subsection{Results}

@@

\subsubsection{Average fixation duration on the robot during observation phase
vs.~condition}

@@

\subsubsection{First improvement vs.~condition}

@@

\subsubsection{Average fixation duration on the reference side during interaction
phase vs.~condition}

@@

\subsubsection{First improvement vs number of fixations on reference side}
